Data Management Plan

### 2019-07-31 Data_Management_Plan.tex
fiel changes

\documentclass[doc]{apa6}
\captionsetup{singlelinecheck=on}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{hyperref}
\bibliographystyle{apacite}
\usepackage{apacite}
\usepackage{color}
\usepackage{tabularx,colortbl}
\usepackage{textcomp}
\usepackage{eurosym}
\usepackage{pdflscape}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{afterpage}
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{rotating}
%\DeclareDelayedFloatFlavor{sidewaystable}{table}
%\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
\usepackage{siunitx}
\usepackage{xfrac}
\singlespacing
\newcommand{\todo}[1] {{\textcolor{red}{#1}}}

@@

The lead author for a paper is responsible for the QA process for the data in that paper, and the data manager for the overall project/dataset is responsible for collating QA information and communicating it to the relevant researchers, or external partners. We will conduct a set of independent replications of key results (e.g., with a simple linear regression in place of a more complicated econometric specification). We will also assess the match between our analysis and publicly available industry or regulator aggregate and summary statistics (e.g., the fraction of people defaulting on their card in any month, etc.). Finally, by linking data sets with public data, we can assess the data quality. For example the prevalence of cash advance charges on credit cards correlates with the fraction of children receiving free school meals in the public domain School Census data, at the level outbound postcode sectors (all but the last two letters).

In addition, we describe specific QA for specific datasets. Financial services in the UK have statutory duties with regard to the collation and maintenance of accurate records under the European Credit Directive and as part of their broader obligations under the Data Protection Act. Thus Barclays and Lloyds have their own internal quality assurance process, as do the credit card providers who have shared data with us in collaboration with the UK Cards Association and the data aggregator Argus. The police has a statutory duty to report statistics (e.g., recorded crime, stop and search) to the Home Office.

@@

\subsection{Data Collected by Us}

Any personal data collection will require and be governed by University of Warwick Humanities and Social Sciences Research Ethics Committee, in addition to any other funder requirements. Data will be held for 10 years from date of last use/access by a third party [EPSRC Expectation VII]. Data will not publicly accessible [EPSRC Expectation II, Expectation VI]. Meta-data will be publicly published, including access statement detailing the route to access [EPSRC Expectation V, Expectation VI]. UK Data Protection Act compliance responsibilities are undertaken by University of Warwick.

\section{Expected Difficulties in Data Sharing}

We will provide full contact details for data collected by third parties as part of the meta data [EPSRC Expectation V, Expectation VI]. Thus other researchers will be able to request the same or additional extracts. For data collected by us, data will be freely available and will be deposited at the UK Data Archive. We will use standard CSV file formats with accompanying README files detailing the column headings. For confidential and/or sensitive data collected by us, sharing is limited to metadata and a statement indicating that data access was under legal agreement and that ``compelling legal or ethical reasons exist to protect access to the data''. Confidential or sensitive data will not be publicly available [EPSRC Expectation II, Expectation VI].

\section{Copyright/Intellectual Property Right}

The data provided by third parties remains the property of the industry partners and these rights are not transferable.

@@

\section{University and Other Relevant Bounding Policies}

Warwick works with confidential and sensitive data every day from a wide range of sources (e.g., credit card records, medical records, police and security services data). As employees of Warwick all researchers are bound by:

\begin{itemize}
	\item The University's obligations under UK Data Protection Legislation
	\item Locally by University data protection policies
	\item The University research ethics committees specialising in the use of human data in the social sciences
	\item The professional bodies for Psychology and Economics in the UK
	\item The ethical requirements of the scientific journals in which they publish
\end{itemize}

Relevant links are:

\begin{itemize}
	\item All lab members should be aware of \href{https://warwick.ac.uk/services/idc/}{University policies} and their obligations under those policies
	\item British Psychological Society \href{https://www.bps.org.uk/news-and-policy/bps-code-ethics-and-conduct}{Code of Conduct}
	\item University \href{http://www2.warwick.ac.uk/services/ris/research\_integrity/researchethicscommittees/hssrec/}{HSSREC}
	\item \href{https://epsrc.ukri.org/files/aboutus/standards/clarificationsofexpectationsresearchdatamanagement/}{EPSRC standards}
\end{itemize}

>>>>

\documentclass[doc]{apa6}
\captionsetup{singlelinecheck=on}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{hyperref}
\bibliographystyle{apacite}
\usepackage{apacite}
\usepackage{color}
\usepackage{tabularx,colortbl}
\usepackage{textcomp}
\usepackage{eurosym}
\usepackage{pdflscape}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{afterpage}
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{rotating}
%\DeclareDelayedFloatFlavor{sidewaystable}{table}
%\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
\usepackage{siunitx}
\usepackage{xfrac}
\singlespacing
\newcommand{\todo}[1] {{\textcolor{red}{#1}}}
\usepackage[margin=0.2in]{geometry}

@@

The lead author for a paper is responsible for the QA process for the data in that paper, and the data manager for the overall project/dataset. The data manager is also responsible for collating QA information and communicating it to the relevant researchers, or external partners. We will conduct a set of independent replications of key results (e.g., with a simple linear regression in place of a more complicated econometric specification). We will also assess the match between our analysis and publicly available industry or regulator aggregate and summary statistics (e.g., the fraction of people defaulting on their card in any month, etc.). Finally, by linking data sets with public data, we can assess the data quality. For example the prevalence of cash advance charges on credit cards correlates with the fraction of children receiving free school meals in the public domain School Census data, at the level outbound postcode sectors (all but the last two letters).

@@

@@
